Two Mode Networks and Relational Similarity

### 2023-08-31 analysis.qmd
Updated analysis, functions, and added bonacich similarity and correspondence plots

```{r Main Plot}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 7, k.c = 5, d.r = 9, d.c = 9)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmCA.res$sim.plot.r + theme(axis.text.x = element_blank())
    f <- tmCA.res$sim.plot.c + theme(axis.text.x = element_blank())
    g <- tmCA.res$corr.plot

>>>>

```{r}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 6, d.c = 6, b.r = 4, b.c = 4)
    a <- tmCA.res$bon.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$bon.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$bon.corr.plot

    png(file = here("Plots", "bon-sim.png"), width=950, height=700)
        (a | b) / c + plot_annotation(tag_levels = "a")
    dev.off() 
```

```{r Main Plot}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 9, d.c = 9)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmCA.res$sim.plot.r + theme(axis.text.x = element_blank())
    f <- tmCA.res$sim.plot.c + theme(axis.text.x = element_blank())
    g <- tmCA.res$corr.plot
